Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-15 article.tex
Spellcheck

\richel{Check against stupidity}
All nucleated cells in humans present randomly sampled polypeptide
fragments to the surroundings of the cell using MHC class I molecules.
If a cell gets infected by a virus, also the virus' polypeptides
will be presented at the cell surface. The viral antigen is detected 
by cytotoxic T lymphocytes, which will kill the infected cell.

@@

We found that the percentages of epitopes overlapping 
with TMHs for a human and Mycopasma proteome are 
[similar/different]. In other words, the
epitopes that MHC-I presents are [as/not as] likely 
to be derived from TMH within either a human host and its bacterial pathogen.

>>>>

\richel{Check against stupidity}
All nucleated cells in humans present randomly sampled polypeptides
fragments to the surroundings of the cell using MHC class I molecules.
If a cell gets infected by a virus, also the virus' polypeptides
will be presented at the cell surface. The viral antigen is detected 
by cytotoxic T lymphocytes, which will kill the infected cell.

@@

We found that the percentages of epitopes overlapping 
with TMHs for a human and Mycoplasma proteome are 
[similar/different]. In other words, the
epitopes that MHC-I presents are [as/not as] likely 
to be derived from TMH within either a human host and its bacterial pathogen.
